% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{resume} 
% the margin option causes section titles to appear to the left of body text 
%\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

 
\name{Parker Knight}
 
\address{1000 S.W. 29th Street \\ Ocala, FL 34471 }
\address{(352) 207-7439 \\ pknight24@ufl.edu}

 
\begin{document} 
 
\begin{rSection}{Education} 
B.S. in Mathematics, University of Florida, Gainesville, FL \\
Expected Graduation: December 2020 \\
GPA: 3.98

\end{rSection}


\begin{rSection}{Experience}

\begin{rSubsection}{Research Assistant}{Aug. 2019 - Present}{Bacher Group, Dept. of
Biostatistics, University of Florida}{Gainesville, FL}
  \item Designed algorithms and software for efficient visualizations
    of DNA methylation data
  \item Analyzed single-cell RNA-seq data and presented results to
    investigators with scientific figures
\end{rSubsection}

\begin{rSubsection}{Research Intern}{June 2019 - Aug. 2019}{Fred Hutchinson Cancer Research Center}
{Seattle, WA}
  \item Analyzed diverse \textit{omics} data sets and communicated results to
    lead statisticians and Principal Investigators
   \item Developed an R package for optimizing high dimensional,
      doubly-structured regression models
\end{rSubsection}

\begin{rSubsection}{Software Engineer Intern}{May 2018 - Aug. 2018}{ITProTV}{Gainesville, FL}
 \item Developed REST API endpoints used across a microservice architecture
 \item Wrote front-end features used directly in customer-facing products
 \item Collaborated with team members, including participation in sprint planning sessions and pair programming
\end{rSubsection} 

\begin{rSubsection}{Research Assistant}{April 2018 - April 2019}{Febo Lab, McKnight Brain Institute}{Gainesville, FL}
      \item Designed and developed audio processing pipeline for analysis of animal vocalizations, including filtering and feature extraction
      \item Executed machine learning classification of complex audio data to study the behavioral effects of drug treatments
      \item Processed resting state fMRI images for use in functional connectivity studies
\end{rSubsection}

 %  {\bf Research Programmer} \\ Digital Worlds Institute, University of
 %  Florida, Gainesville, FL \hfill Jan. 2018 - April 2019
 %  \begin{itemize} \itemsep -2pt 
 %      \item Built visual learning games with WebVR technologies
 %      \item Practiced remote development techniques with Git and weekly video calls 
 %  \end{itemize}


\begin{rSubsection}{Research Assistant}{Sept. 2016 - April 2019}{Bruijnzeel Lab, McKnight Brain Institute}{Gainesville, FL}
     \item Planned and executed behavioral neuroscience experiments, including Large Open Field, Elevated Plus Maze, and Novel Object Recognition tests
     \item Analyzed behavioral data using clustering methods and hypothesis testing
     \item Communicated results to Principal Investigators through visualizations, formal reports, and presentations
     \end{rSubsection}
     
\end{rSection}

\begin{rSection}{Involvement}
  
\begin{rSubsection}{Learning Assistant}{Aug. 2018 - April 2019}{Dept. of Mathematics, University of Florida}{Gainesville, FL}
      \item Lead group discussion of course material with undergraduate students
      \item Assisted students with homework and classwork
      \item Courses taught: Analytical Geometry and Calculus 1, Analytical Geometry and Calculus 2 \\ \\ 
  \end{rSubsection}

 \begin{rSubsection}{Director of Multimedia}{May 2018 - April 2019}{Center for Undergraduate Research, University of Florida}{Gainesville, FL}
    \item Coordinated and led production of video content to promote research-related events
    \item Met with faculty and other board members to manage the Center's website content
\end{rSubsection}


\begin{rSubsection}{Peer Advisor}{August 2017 - May 2018}{Center for Undergraduate Research, University of Florida}{Gainesville, FL}
    \item Held office hours twice weekly to provide assistance to undergraduate students in finding research opportunities on campus
    \item Advised students in enhancing their research experience through scholarships and presentations
  \end{rSubsection}

\end{rSection}
  

\begin{rSection}{Publications} % these are in APA format!
  \begin{itemize}
    \item Chellian, R., Behnood-Rod, A., Wilson, R., Wilks, I.,
      \textbf{Knight, P.}, Febo, M., Bruijnzeel, A. W. (2020). Exposure to
      smoke from high-but not low-nicotine cigarettes leads to signs
      of dependence in male rats and potentiates the effects of
      nicotine in female rats. \textit{Pharmacology Biochemistry and Behavior},
      172998.
    \item Chellian, R., Wilson, R., Polmann, M., \textbf{Knight, P.},
      Behnood-Rod, A., Bruijnzeel, A. W. (2020). Evaluation of sex
      differences in the elasticity of demand for nicotine and food in
      rats. \textit{Nicotine and Tobacco Research}, 22(6), 925-934.
    \item Tan, S., Xue, S., Behnood-Rod, A., Chellian, R., Wilson, R.,
      \textbf{Knight, P.}, Panunzio, S., Lyons, H., Febo, M., Bruijnzeel, A. W. (2019). Sex differences in
      the reward deficit and somatic signs associated with
      precipitated nicotine withdrawal in rats. \textit{Neuropharmacology},
      160, 107756.
    \item Bruijnzeel, A. W., \textbf{Knight, P.}, Panunzio, S., Xue, S.,
      Bruner, M. M., Wall, S. C., Pompilus, M., Febo, M., Setlow, B. (2019). Effects in
      rats of adolescent exposure to cannabis smoke or THC on
      emotional behavior and cognitive function in
      adulthood. \textit{Psychopharmacology}, 236(9), 2773-2784.
    \end{itemize}
    \end{rSection}

\begin{rSection}{Presentations}
  \begin{itemize} % \itemsep -2pt
    \item ''Estimation and inference for high dimensional,
      doubly-structured regression models'' \\ Fall Undergraduate
      Research Symposium, Gainesville, FL \hfill October 2019
      \item "Virtual Reality-based Learning Games for Computer Science Education" \\ Spring Undergraduate Research Symposium, Gainesville, FL \hfill April 2019 
      \item "Sex Differences in Rodent Behavior: a Hierarchical Clustering Analysis" \\ UF College of Medicine Poster Session, Gainesville, FL \hfill February 2019
      \item "Machine Learning Classification of Ultrasonic Animal Vocalizations" \\Fall Undergraduate Research Symposium, Gainesville, FL \hfill November 2018
      \item "Adolescent Cannabis Smoke Exposure Does Not Affect Anxiety or Depressive-like Behavior in Male and Female Rats in Adulthood"\\Center for Addiction Research and Education Spring Symposium, Gainesville, FL \hfill April 2018
      \item"Long Term Behavioral Effects of Cannabis Smoke in Rats"\\Fall Undergraduate Research Symposium, Gainesville, FL \hfill November 2017
  \end{itemize}
  \end{rSection}

  \begin{rSection}{Honors and Awards}
  Honorable Mention in COMAP's Mathematical
  Contest in Modeling \hfill 2020 \\
Cold Spring Harbor Laboratory Undergraduate Research Program (Declined) \hfill 2019 \\
Fred Hutchinson Summer Undergraduate Research Program (\$4750) \hfill 2019 \\
College of Liberal Arts and Sciences Dean's List \hfill All Semesters \\
  Anderson Scholar with High Distinction \hfill 2018 \\
  University Scholars Research Scholarship (\$1750) \hfill 2018 \\
  University Scholars Research Scholarship (\$1750) \hfill 2017 \\
Student Honors Organization \hfill 2016 
 \end{rSection}

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\begin{rSection}{Skills}
   \begin{tabular}{l p{3in}}
    \underline{Languages:} & R, Python, Haskell, C++, JavaScript \\
     \underline{Software:} & Linux, Git, Docker, SQLite
 \end{tabular}
\end{rSection}

\end{document} 



