
% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{resume} 
% the margin option causes section titles to appear to the left of body text 
%\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

 
\name{Parker Knight}
 
\address{1000 S.W. 29th Street \\ Ocala, FL 34471 }
\address{(352) 207-7439 \\ pknight24@ufl.edu}

 
\begin{document} 
 
\begin{rSection}{Education} 
B.S. in Mathematics, University of Florida, Gainesville, FL \\
Expected Graduation: December 2020 \\
GPA: 3.98

\end{rSection}


\begin{rSection}{Experience}

\begin{rSubsectionEmpty}{Research Assistant}{Aug. 2019 - Present}{Bacher Group, Dept. of
Biostatistics, University of Florida}{Gainesville, FL}
\end{rSubsectionEmpty}

\begin{rSubsectionEmpty}{Research Intern}{June 2019 - Aug. 2019}{Randolph
    Group, Fred Hutchinson Cancer Research Center}
{Seattle, WA}
\end{rSubsectionEmpty}

\begin{rSubsectionEmpty}{Software Engineer Intern}{May 2018 - Aug. 2018}{ITProTV}{Gainesville, FL}
\end{rSubsectionEmpty} 

\begin{rSubsectionEmpty}{Research Assistant}{April 2018 - April 2019}{Febo Lab, McKnight Brain Institute}{Gainesville, FL}
\end{rSubsectionEmpty}

 %  {\bf Research Programmer} \\ Digital Worlds Institute, University of
 %  Florida, Gainesville, FL \hfill Jan. 2018 - April 2019
 %  \begin{itemize} \itemsep -2pt 
 %  \end{itemize}

\begin{rSubsectionEmpty}{Research Assistant}{Sept. 2016 - April 2019}{Bruijnzeel Lab, McKnight Brain Institute}{Gainesville, FL}
     \end{rSubsectionEmpty}
     
\end{rSection}

\begin{rSection}{Published Work} % these are in APA format!
  \begin{rSubsection}{Journal Articles}{}{}{}
    \item \textbf{Knight, P.}, Pardo, C.E., Darst, R.P, Riva, A.,
      Gauthier, M.L., Kladde, M.P., Bacher, R. (2020). methylscaper:
      an R/Shiny app for joint visualization of DNA methylation and
      nucleosome occupancy in single-molecule and single-cell
      data. \textit{Submitted to Bioinformatics.}
    \item Bacher, R., Chu, L., Argus, C., Bolin, J., \textbf{Knight,
        P.}, Thomson, J., Stewart, R., Kendziorski,
      C. (2020). Enhancing biological signals and detection rates in
      single-cell RNA-seq experiments with cDNA library
      equalization. \textit{Submitted to Nucleic Acids Research}.
    \item Darden, D.B., Bacher, R., Brusko, M.A., \textbf{Knight, P.},
      ... \& Efron, P. (2020). Single cell RNA-seq of human myeloid derived suppressor
      cells in late sepsis reveals multiple subsets with unique
      transcriptional responses: a pilot study. \textit{Accepted in
        Shock: Injury, Inflammation, and Sepsis: Laboratory and
        Clinical Approaches}. 
    \item \textbf{Knight, P.}, Chellian, R., Wilson, R., Behnood-Rod,
      A., Panunzio, S., Bruijnzeel, A.W. (2020). Comprehensive evaluation of sex differences in the elevated
      plus-maze test and large open field test in adult Wistar
      rats. \textit{Submitted to Behavioural Brain Research.}
    \item Chellian, R., Behnood-Rod, A., Wilson, R., Wilks, I.,
      \textbf{Knight, P.}, Febo, M., Bruijnzeel, A. W. (2020). Exposure to
      smoke from high-but not low-nicotine cigarettes leads to signs
      of dependence in male rats and potentiates the effects of
      nicotine in female rats. \textit{Pharmacology Biochemistry and Behavior},
      172998.
    \item Chellian, R., Wilson, R., Polmann, M., \textbf{Knight, P.},
      Behnood-Rod, A., Bruijnzeel, A. W. (2020). Evaluation of sex
      differences in the elasticity of demand for nicotine and food in
      rats. \textit{Nicotine and Tobacco Research}, 22(6), 925-934.
    \item Tan, S., Xue, S., Behnood-Rod, A., Chellian, R., Wilson, R.,
      \textbf{Knight, P.}, Panunzio, S., Lyons, H., Febo, M., Bruijnzeel, A. W. (2019). Sex differences in
      the reward deficit and somatic signs associated with
      precipitated nicotine withdrawal in rats. \textit{Neuropharmacology},
      160, 107756.
    \item Bruijnzeel, A. W., \textbf{Knight, P.}, Panunzio, S., Xue, S.,
      Bruner, M. M., Wall, S. C., Pompilus, M., Febo, M., Setlow, B. (2019). Effects in
      rats of adolescent exposure to cannabis smoke or THC on
      emotional behavior and cognitive function in
      adulthood. \textit{Psychopharmacology}, 236(9), 2773-2784.
    \end{rSubsection}
    \begin{rSubsection}{Software}{}{}{}
	\item methylscaper: An R package and Shiny app for visualizing methylation state data.     Available on GitHub.
	\item KPR: An R package for fitting kernel-penalized regression models with valid inference. Available on GitHub.
	\item scaffold: Experiment-driven simulations of single-cell RNA-seq data. Available on GitHub.
    \end{rSubsection}
    \end{rSection}

\begin{rSection}{Presentations}
  \begin{rSubsection}{Poster Presentations}{}{}{} % \itemsep -2pt
    \item ``Estimation and inference for high dimensional,
      doubly-structured regression models'', Fall Undergraduate
      Research Symposium, Gainesville, FL, October 2019
    \item  ``Estimation and inference for high dimensional,
      doubly-structured regression models'', Fred Hutchinson Cancer Research Center Poster Session, August 2019
      \item ``Virtual Reality-based Learning Games for Computer Science Education'', Spring Undergraduate Research Symposium, Gainesville, FL, April 2019 
      \item ``Sex Differences in Rodent Behavior: a Hierarchical Clustering Analysis'', UF College of Medicine Poster Session, Gainesville, FL, February 2019
      \item ``Machine Learning Classification of Ultrasonic Animal Vocalizations'', Undergraduate Research Symposium, Gainesville, FL, November 2018
      \item ``Adolescent Cannabis Smoke Exposure Does Not Affect
        Anxiety or Depressive-like Behavior in Male and Female Rats in
        Adulthood'', Center for Addiction Research and Education Spring Symposium, Gainesville, FL, April 2018
      \item``Long Term Behavioral Effects of Cannabis Smoke in Rats'',
        Fall Undergraduate Research Symposium, Gainesville, FL, November 2017
  \end{rSubsection}
  \end{rSection}

  \begin{rSection}{Honors and Awards}
  Honorable Mention in COMAP's Mathematical
  Contest in Modeling \hfill 2020 \\
  Fred Hutch Translational Data Science IRC Planning Funds (\$5000) \hfill 2019 \\
  Phi Beta Kappa Academic Honor Society \hfill 2019 \\
  Fred Hutchinson Summer Undergraduate Research Program (\$4750) \hfill 2019 \\
  College of Liberal Arts and Sciences Dean's List \hfill All Semesters \\
  UF Anderson Scholar with High Distinction \hfill 2018 \\
  UF University Scholars Research Scholarship (\$1750) \hfill 2018 \\
  UF University Scholars Research Scholarship (\$1750) \hfill 2017 \\
  UF Student Honors Organization \hfill 2016 
 \end{rSection}

 
\begin{rSection}{Academic Service}
  
\begin{rSubsection}{Learning Assistant}{Aug. 2018 - April
    2019}{Dept. of Mathematics, University of Florida}{Gainesville,
    FL}
   \item Courses taught: Analytical Geometry and Calculus 1, Analytical
    Geometry and Calculus 2
  \end{rSubsection}

 \begin{rSubsectionEmpty}{Director of Multimedia}{May 2018 - April 2019}{Center for Undergraduate Research, University of Florida}{Gainesville, FL}
\end{rSubsectionEmpty}


\begin{rSubsectionEmpty}{Peer Advisor}{August 2017 - May 2018}{Center for Undergraduate Research, University of Florida}{Gainesville, FL}
  \end{rSubsectionEmpty}

\end{rSection}
  

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\begin{rSection}{Skills}
   \begin{tabular}{l p{3in}}
    \underline{Languages:} & R, Python, Haskell, C++, JavaScript \\
     \underline{Software:} & Linux, Git, Docker, SQLite
 \end{tabular}
\end{rSection}

\end{document} 



